
\noindent{\bf Education and Training}
\begin{itemize}
\setlength{\itemsep}{0.2pt}
\item
University of Illinois at Urbana-Champaign, Ph.D. in Computer Science, January 2000
\item
Wake Forest University, B.S. {\it summa cum laude} in Computer Science, May 1995
\end{itemize}


\noindent{\bf Research and Professional Experience}
\begin{itemize}
\setlength{\itemsep}{0.2pt}
\item

Associate Professor, University of Oregon, 
Computer and Information Science Department, since Sept. 2015

\item
Assistant Professor, University of Oregon, 
Computer and Information Science Department, Sept. 2013 -- Sept 2015

\item 
Computer Scientist, Argonne National Laboratory,
Mathematics and Computer Science Division, Mar. 2006 -- Aug. 2013

\item 
Assistant Computer Scientist, Argonne National Laboratory,
Mathematics and Computer Science Division, Oct. 2001 -- Mar. 2006

%\item 
%Senior Fellow, Computation Institute,
%University of Chicago and Argonne National Laboratory, since Apr. 2004
\item
Postdoctoral Fellow, Argonne National Laboratory,
Mathematics and Computer Science Division, Nov. 1999 -- Sept. 2001

\end{itemize}


\noindent{\bf Selected Publications}
\begin{enumerate}
\setlength{\itemsep}{0.2pt}

\item %{HPCC}
K. Sood, B. Norris, and E. Jessup. 
\newblock Comparative performance modeling of parallel 
preconditioned Krylov methods. 
\newblock {\em Proceedings the 18th IEEE International 
Conference on High
Performance Computing and Communications (HPCC)}, 2017. Best paper finalist.

\item %{sisc16}
E.~Jessup, P.~Motter, B.~Norris, and K.~Sood.
\newblock Performance-based numerical solver selection in the {L}ighthouse
  framework.
\newblock {\em SIAM Journal on Scientific Computing}~38, 2016,
  \url{http://epubs.siam.org/toc/sjoce3/38/5}.

\item %{naecon15}
M.~Rashti, G.~Sabin, and B.~Norris.
\newblock Power and energy analysis and modeling of high performance computing
  systems using {WattProf}.
\newblock {\em Proceedings of the 2015 IEEE National Aerospace and Electronics
  Conference (NAECON)}, July 2015.

\item   %{bto-toms15}
T.~Nelson, G.~Belter, J.~Siek, E.~Jessup, and B.~Norris.
\newblock Reliable generation of high-performance matrix algebra.
\newblock {\em ACM Transactions on Mathematical Software}~41, June 2015.

\item   %{icpads14}
N.~Chaimov, B.~Norris, and A.~Malony.
\newblock Toward multi-target autotuning for accelerators.
\newblock {\em Proceedings of the 20th IEEE International Conference on
  Parallel and Distributed Systems, December 16-19, 2014, Hsinchu, Taiwan},
  2014.
  % \url{http://ix.cs.uoregon.edu/~norris/icpads14.pdf}.

\item    %{Lighthouse-eigen14}
R.~Nair, S.-L. Bernstein, E.~Jessup, and B.~Norris.
\newblock Generating customized sparse eigenvalue solutions with {L}ighthouse.
\newblock {\em Proceedings of the Ninth International Multi-Conference on
  Computing in the Global Information Technology June 22 - 17, 2014, Seville,
  Spain}, 2014.

\item %\bibitem{sisc13}
C.~Choudary, J.~Godwin, J.~Holewinski, D.~Karthik, D.~Lowell, A.~Mametjanov,
  B.~Norris, G.~Sabin, and P.~Sadayappan.
\newblock Stencil-aware {GPU} optimization of iterative solvers.
\newblock {\em SIAM Journal on Scientific Computing} 35(5):S209--S228, October
  2013, \url{http://www.mcs.anl.gov/uploads/cels/papers/P3008-0712.pdf}.

%%SABIN COMMENT FOR SPACE  
%% \item
%% A.~Mametjanov, D.~Lowell, C.-C. Ma, and B.~Norris.
%% \newblock Autotuning stencil-based computations on {GPU}s.
%% \newblock {\em Proceedings of IEEE Cluster 2012}, 2012,
%%   \url{http://www.mcs.anl.gov/uploads/cels/papers/P2094-0512.pdf}.

\item
S.~H.~K. Narayanan, B.~Norris, and P.~D. Hovland.
 \newblock Generating performance bounds from source code.
 \newblock {\em Proceedings of the First International Workshop on Parallel
   Software Tools and Tool Infrastructures (PSTI 2010)}, 9 2010.
  \url{http://www.mcs.anl.gov/uploads/cels/papers/P1685.pdf}.

%\item
%V.~Bui, B.~Norris, and L.~C. McInnes.
%\newblock An automated component-based performance experiment environment.
%\newblock {\em Proceedings of the 2009 Workshop on Component-Based High
%  Performance Computing (CBHPC 2009)}, Nov. 2009,
%  \url{http://www.mcs.anl.gov/uploads/cels/papers/P1666.pdf}.
%\newblock Also available as Preprint ANL/MCS-P1666-0809.

%\item
%B.~Norris, A.~Hartono, E.~Jessup, and J.~Siek.
%\newblock Generating empirically optimized composed matrix kernels from Matlab
%  prototypes.
%  \newblock {\em Proceedings of the International Conference on Computational
%    Science 2009}, 2009,
%      \url{http://www.mcs.anl.gov/uploads/cels/papers/P1581.pdf}.

\item
A.~Hartono, B.~Norris, and P.~Sadayappan.
\newblock Annotation-based empirical performance tuning using {Orio}.
\newblock {\em Proceedings of the 23rd IEEE International Parallel \&
  Distributed Processing Symposium}, 2009,
    \url{http://www.mcs.anl.gov/uploads/cels/papers/P1556.pdf}.

\item 
K.~A. Huck, O.~Hernandez, V.~Bui, S.~Chandrasekaran, B.~Chapman, A.~D. Malony,
  L.~C. McInnes, and B.~Norris.
\newblock {Capturing performance knowledge for automated analysis}.
\newblock {\em {International Conference for High Performance Computing,
  Networking, Storage and Analysis (SC'08)}}, 2008.

\item
W.~Elwasif, B.~Norris, B.~Allan, and R.~Armstrong.
\newblock Bocca: {A} development environment for HPC components.
\newblock in {\em Proceedings of HPC-GECO/CompFrame'07, October
  21-22, 2007, Montreal, Qu\'ebec, Canada}. ACM, 2007.

\item
D.~R. Dechow, B.~Norris, and J.~Amundson.
\newblock The {C}ommon {C}omponent {A}rchitecture for particle accelerator
  simulations.
\newblock in {\em Proceedings of HPC-GECO/CompFrame'07, October
  21-22, 2007, Montreal, Qu\'ebec, Canada}. ACM, 2007.

\item 
B.~Norris, A.~Hartono, and W.~Gropp.
\newblock Annotations for Productivity and Performance Portability.
\newblock in \emph{Petascale computing: {A}lgorithms and applications}.
Chapman \& Hall / CRC Press, Taylor and Francis Group, Computational Science,
2007.

\item
 Characterizing the performance and energy attributes of scientific
 simulations, S.~Akioka, K.~Malkowski, P.~Raghavan, M.~J. Erwin,
 L.~C. McInnes, and B.~Norris, in {\em Computational Science ICCS
 2006: 6th International Conference, Reading, UK, May 28-31, 2006,
 Proceedings, Part I, vol. 3991}, pp. 242--249.  Springer, Lecture Notes in
 Computer Science, 2006.

\item 
Adaptive software for scientific computing: Co-managing
quality-performance-power tradeoffs, P. Raghavan, M. J. Irwin,
L. C. McInnes, and B. Norris, in {\em Proceedings of the IEEE International Parallel
\& Distributed Processing Symposium 2005 (CDROM)}. IEEE Computer Society Press,
2005.

%\item P.~Hovland, B.~Norris, and B.~Smith.
%Making automatic differentiation truly automatic: {C}oupling {PETSc}
%  with {ADIC}.
%{\em Future Generation Computer Systems} 21(8):1426--1438, 2005.
%  \url{http://dx.doi.org/10.1016/j.future.2004.11.008}.
%
%\item
%C.~Bischof, P.~Hovland, and B.~Norris.
%Implementation of automatic differentiation tools.
%{\em Proceedings of the 2002 {ACM} {SIGPLAN} Workshop on Partial
%Evaluation and Semantics-Based Program Manipulation ({PEPM}-02)}, vol.~37,
%  pp. 98--107. ACM Press, ACM SIGPLAN Notices~3, Jan. ~14--15 2002.
%

%\end{tenumerate}

%\newpage
%\itemskip
%\noindent{\bf Five Other Significant Publications}
%\begin{enumerate}

%\item
%Parallel PDE-Based simulations using the Common Component
%  Architecture,
%L.~C. McInnes, B.~A. Allan, R.~Armstrong, S.~J. Benson, D.~E. Bernholdt, T.~L.
%  Dahlgren, L.~F. Diachin, M.~Krishnan, J.~A. Kohl, J.~W. Larson, S.~Lefantzi,
%  J.~Nieplocha, B.~Norris, S.~G. Parker, J.~Ray, and S.~Zhou,
%in {\em Numerical Solution of Partial Differential Equations on Parallel
%  Computers}, pp. 327--381. Springer, Lecture Notes in Computational Science
%  and Engineering~51, 2006.
%\newblock Preprint ANL/MCS-P1179-0704.

%\item 
%A Component architecture for high-performance scientific computing, 
%D.~E. Bernholdt, B.~A. Allan, R.~Armstrong, F.~Bertrand, K.~Chiu, T.~L.
%Dahlgren, K.~Damevski, W.~R. Elwasif, T.~G.~W. Epperly, M.~Govindaraju, D.~S.
%Katz, J.~A. Kohl, M.~Krishnan, G.~Kumfert, J.~W. Larson, S.~Lefantzi, M.~J.
%Lewis, A.~D. Malony, L.~C. McInnes, J.~Nieplocha, B.~Norris, S.~G. Parker,
%J.~Ray, S.~Shende, T.~L. Windus, and S.~Zhou, 
%{\em International Journal of High Performance Computing Applications}, 
%Nov. 2005.

%%SABIN COMMENT FOR SPACE
%% \item
%% B.~Norris.
%% \newblock Software architecture issues in scientific component development.
%% \newblock {\em Applied Parallel Computing: 7th International Conference, PARA
%%   2004, Lyngby, Denmark, June 20-23, 2004. Revised Selected Papers}, vol. 3732,
%%   pp. 629--636. Springer Berlin / Heidelberg, Lecture Notes in Computer
%%   Science, 2006.

%\item
%B.~Norris, J.~Ray, R.~C. Armstrong, L.~C. McInnes, D.~E. Bernholdt, W.~R.
%  Elwasif, A.~D. Malony, and S.~Shende.
%\newblock Computational quality of service for scientific components.
%\newblock {\em Proceedings of the International Symposium on Component-Based
%  Software Engineering (CBSE7), Edinburgh, Scotland, May 24--25, 2004}, vol.
%  3054, pp. 264--271. Springer, Lecture Notes in Computer Science, 2004.

%\item
%Faster PDE-Based simulations using robust composite linear solvers,
%S. Bhowmick, P. Raghavan, L. McInnes, and B. Norris, {\em Future Generation
%Computer Systems} 20(3):373--387, 2004.

%\item
%The role of multi-method linear solvers in PDE-based simulations,
%S. Bhowmick, L. McInnes,  B. Norris, and P. Raghavan, in {\em
%Proceedings of the  2003 International  Conference on Computational Science and its
%Applications, ICCSA 2003, Montreal, Canada May 18 - May 21, 2003}.
%Lecture notes in Computer Science 2677,
%Editors V. Kumar, M. L. Gavrilova C. J. K. Tan, and P. L'Ecuyer, pp. 828--839, 2003.

\end{enumerate}

%\itemskip
%\noindent{{\bf Honor and Professional Societies} (member since)}
%\begin{description}
%\item
%National Honor Society (1991); Phi Beta Kappa (1994); SIAM (1998); ACM (1998); IEEE Computer Society (1999)
%\end{description}

\noindent{{\bf Synergistic Activities}}
\begin{itemize}
\setlength{\itemsep}{0.2pt}
\item Argonne PI in the DOE SciDAC-3 Institute for Sustained Performance, Energy, and Resilience (SUPER).
\item Editor, {\em Automatic Differentiation: {A}pplications, Theory, and Implementations}, vol.~50.
 Lecture Notes in Computational Science and Engineering. Springer, New York, NY, 2005.
%\item Member of the Argonne Women in Science and Technology Steering Committee, since August 2006.
\item SIAM Activity Group on Supercomputing, Secretary (2006--2008), Vice-chair (2010--2012).
\item Organizing committee member for the Fourth International Conference on Automatic Differentiation (AD'2004), July 2004.
\item Organizer of a minisymposium on high-performance components at the SIAM PP'04 conference
\item Program Committee, SC'10, QoSA'09 and '10, 2004 and 2008 SIAM Parallel Processing , CBHPC'08, Compframe'07, HPC-GECO'06, SAC'03, ICCSA'03, HICSS (multiple years).
\item Reviewer for Parallel Computing, IJHPCA, SISC, DOE and NSF proposals.
\end{itemize}



\noindent{\bf Doctoral Advisor:} 
Michael T. Heath, University of Illinois at Urbana-Champaign (UIUC)

\noindent{\bf Postdoctoral Advisor:} 
William Gropp, Argonne National Laboratory (currently at UIUC)
%\tinyskip
%\noindent{\bf Thesis advisees:} Sri Hari Krishna Narayanan, The Pennsylvania State University (co-advisee), Ph.D. 200?

\noindent{\bf Post-graduate advisees:}  Li Li (Argonne), Sri Hari Krishna Narayanan (Argonne),  Qian Zhu (ANL), Azamat Mametjanov (ANL)


